Joker: A Unified Interaction Model For Web Customization

### 2021-08-02 paper.tex
First pass to get paper under 6 pages

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage[sort, numbers]{natbib}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

% Make font size smaller in bibliography, as per:
% https://tex.stackexchange.com/questions/386709/proper-usage-of-biblatex-ieee-biblatex-style-in-an-ieeetran-document
\renewcommand*{\bibfont}{\footnotesize}

% begin pandoc tex stuff

@@

% end pandoc tex stuff

\begin{document}

\title{Joker: A Unified Interaction Model For Web Customization}

% removing authors for anonymous submission

% \author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID}
% \and
% \IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID}
% \and
% \IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID}
% \and
% \IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID}}

\maketitle

\begin{abstract}
Tools that enable end-users to customize websites typically use a
two-stage workflow: first, users extract data into a structured form;
second, they use that extracted data to augment the original website in
some way. This two-stage workflow poses a usability barrier because it
requires users to make upfront decisions about what data to extract,
rather than allowing them to incrementally extract data as they augment
it.

In this paper, we present a new, unified interaction model for web
customization that encompasses both extraction and augmentation. The key
idea is to provide users with a spreadsheet-like formula language that
can be used for both data extraction and augmentation. We also provide a
programming-by-demonstration (PBD) interface that allows users to create
data extraction formulas by clicking on elements in the website. This
model allows users to naturally and iteratively move between extraction
and augmentation.

To illustrate our unified interaction model, we have implemented a tool
called Joker which is an extension of Wildcard, a prior web
customization system. Through case studies, we show that Joker can be
used to customize many real-world websites. We also present a formative
user study with five participants, which showed that people with a wide
range of technical backgrounds can use Joker to customize websites, and
also revealed some interesting limitations of our approach. Finally, we
present a heuristic evaluation of our design using the Cognitive
Dimensions framework.
\end{abstract}

\begin{IEEEkeywords}
end-user web customization, programming-by-demonstration, spreadsheets, end-user web scraping, program synthesis
\end{IEEEkeywords}

@@

Section~\ref{sec:examples} describes a concrete scenario, showing how
Joker enables a user to complete a useful customization task. In
Section~\ref{sec:implementation}, we outline the implementation of our
formula language and user interface, as well as the algorithms used by
our PBD interface.

We have performed three evaluations of our approach, presented in
Section~\ref{sec:evaluation}. First, we describe a suite of case studies
in which we used Joker to extract and augment a variety of websites in
order to characterize its capabilities and limitations. Second, we
describe a formative user study with five participants, which showed
that users were generally able to use Joker to perform useful extraction
and augmentation tasks, but which also uncovered limitations,
particularly for less experienced users trying to extract data from more
complex websites. Finally, we perform a heuristic evaluation of our
design, using the Cognitive Dimensions \citep{blackwell2001} framework.

Joker relates to existing work not only in end-user web customization,
but also in end-user web scraping and program synthesis, which we
discuss in Section~\ref{sec:related-work}. Finally, we discuss
opportunities for future work in Section~\ref{sec:conclusion}.

@@

In this section, we describe Joker's formula language in more detail.
Then, we outline the \emph{wrapper induction} \citep{kushmerick2000}
algorithm that Joker's PBD interface uses to synthesize the row element
and column selectors presented in formulas. Figure~\ref{fig:overview}
illustrates the entire process.

@@

When users demonstrate a specific column value to extract, Joker must
synthesize a program that reflects the user's general intent. This is an
instance of the \emph{wrapper induction} problem of synthesizing a web
data extraction query from examples. Prior work on this topic
\citep{kushmerick2000, furche2016} prioritizes accuracy and robustness
to future changes, which makes sense for a fully automated system, but
can lead to very complex queries. In our work, we chose to prioritize
the readability of queries by less sophisticated users, so that users
can more easily author queries and repair them when they break. We
implemented a set of heuristics inspired by Vegemite \citep{lin2009} for
wrapper induction, described below.

\hypertarget{determining-row-elements}{%
\subsubsection{Determining Row
Elements}\label{determining-row-elements}}

The user starts by demonstrating an element \(v\), representing a value
that should be in the table. From that demonstration, we must find a set
of \emph{row elements} that represent the rows of the table. We could
naively assume that \(parent(v)\) is the row containing \(v\), but often
\(v\) is deeply nested inside its containing row; we must determine
which ancestor of \(v\) is likely to be the row.

Intuitively, we solve this problem by assuming that all rows share some
similar internal structure. In particular, we expect most rows to
contain a value for the demonstrated column. (If there were no missing
data, we'd expect \emph{all} rows to contain data for this column.)

Formally: assume a function \(select(el, s)\) which runs a CSS selector
that returns the set of elements matching \(s\) within \(el\). We
generate a set of plausible candidates \(P\), consisting of pairs of a
row element and a CSS selector:

\(P = \{ (r, s) \mid r \in ancestors(v) \land select(r, s) = \{v\} \}\)

For each candidate \((r, s) \in P\), we compute a weight function \(w\),
which is based on the number of siblings of \(r\) that have ``similar
structure'', defined by checking whether running \(s\) within the
sibling also returns a unique element.

\(w(r, s) = |\{ r' \mid r' \in siblings(r) \land |select(r', s) | = 1 \}|\)

We then choose the candidate with the highest weight. In case of ties,
the candidate closer to \(v\) in the tree (i.e., lower in the tree)
wins. Given a winning candidate \((r, s)\), the full set of row elements
is \(\{r\} \cup siblings(r)\).

\hypertarget{synthesizing-css-selectors-for-column-values}{%
\subsubsection{Synthesizing CSS Selectors For Column
Values}\label{synthesizing-css-selectors-for-column-values}}

Once we have determined the row elements, next we must choose a CSS
selector that will be used to identify the demonstrated value within its
row.

Given a demonstrated value \(v\) within a row element \(r\), we generate
two kinds of plausible selectors:

\begin{itemize}
\tightlist
\item
  selectors using CSS classes, which are manual annotations on DOM
  elements added by the website's programmers, typically for styling
  purposes (e.g.~"item\_\_price")
\item
  selectors using positional indexes within the tree, using the
  \texttt{nth-child} CSS selector (e.g.~\texttt{nth-child(2)},
  representing the second child of an element)
\end{itemize}

The minimum criteria for a plausible selector \(s\) is that it uniquely
identifies the value within the row: \(select(r, s) = \{v\}\). But there
may be many plausible selectors, so we must pick a best one.

We first prioritize selectors using classes, because they tend to be
more robust to changes on the website. A single selector can combine
multiple classes, but we prefer using fewer classes when possible. If no
plausible class-based selector can be generated (for example, if the
relevant elements don't have any classes to query), we fall back to
using a positional index selector. This kind of selector can always be
generated regardless of the contents of the page, but tends to be less
accurate and robust.

@@

We evaluate our interaction model and tool in terms of three research
questions:

\emph{RQ1: What kinds of websites can this model operate effectively
on?} We evaluate this with a suite of case studies that demonstrate its
capabilities and limitations.

\emph{RQ2: How are users of different backgrounds able to use the
system?} We evaluate this with a small formative user study.

\emph{RQ3: What are the essential design dimensions that distinguish
this model from other approaches?} We evaluate this with a heuristic
analysis using the Cognitive Dimensions of Notation framework
\citep{blackwell2001}.

\hypertarget{case-studies}{%
\subsection{Case Studies}\label{case-studies}}

Our first evaluation describes the results of the authors using Joker to
extract data and perform customizations on popular websites. For the
websites on which Joker can be used, we provide the sequence of
interactions needed to achieve the customizations; for the websites on
which Joker fails, we explain the relevant limitations.

\hypertarget{successful-applications}{%
\subsubsection{Successful Applications}\label{successful-applications}}

@@

\emph{Filtering titles of publications on Google Scholar.} We have also
found Joker can be useful for filtering a website's listings based on
the text content of an element in the listing. For example, we have used
Joker to filter the titles of a researcher's publications on their
Google Scholar profile which is not natively supported. First, a user
can extract the titles into a column (\texttt{A}) by demonstration.
Then, the user can write the formula \texttt{Includes(A,\ "compiler")}
that returns whether or not the title contains the keyword ``compiler''.
Finally, the user can sort by this column to get all of the publications
that fit their constraint at the top of the page. We have also used
Joker to filter other text-based directory web pages such as Google
search results and the MIT course catalog, in similar ways.

@@

\hypertarget{limitations}{%
\subsubsection{Limitations}\label{limitations}}

@@

\hypertarget{user-study}{%
\subsection{User Study}\label{user-study}}

We conducted a small formative user study to understand how people would
interact with Joker.

\hypertarget{participants}{%
\subsubsection{Participants}\label{participants}}

We recruited 5 participants with varying backgrounds. 3 participants
were familiar with spreadsheet formulas. 3 participants had extensive
web development experience, 1 had a small amount of prior web
development experience, and 1 had no web development experience. 3
participants had previously extracted data from websites.

\hypertarget{protocol}{%
\subsubsection{Protocol}\label{protocol}}

The participants completed 7 web customization tasks across 2 websites.
All participants attempted all the tasks.

First, we asked participants to customize a website with a relatively
simple HTML structure: the MIT EECS course catalog website. All data
\emph{extraction} on this site can be performed with demonstrations
alone in Joker, although augmentation still requires writing formulas.
The specific tasks were the following: 1a) Extract course titles, 1b)
Extract course prerequisites, 1c) Add a column that indicates whether a
course has a prerequisite \& 1d) Add a column that indicates whether a
course has no prerequisites and is offered in the fall term.

Next, we asked participants to customize a website with a more complex
HTML structure: the search results page for the eBay shopping website.
Due to the website's complexity, demonstrations alone are not sufficient
to extract data; users must also directly edit extraction formulas. The
specific tasks were the following: 2a) Extract title from listings of
Apple iPhones for sale, 2b) Extract the listing price for the phone, \&
2c) Create a column that indicates whether a listing for a phone is
sponsored.

Each session was 60 minutes long and conducted over a recorded video
conference. We started each session with a description of Joker and
provided a brief tutorial of its main features on a sample website not
used in the tasks. There was no time limit for completing the tasks.
Users were encouraged to speak aloud as they worked.

Because some of the tasks build on results of previous tasks, we wanted
to ensure all participants made enough progress to gather useful
feedback. Therefore, whenever a participant got stuck for several
minutes, we recorded why they were stuck and then offered hints on how
to proceed (such as suggestions to read formula documentation or open
the browser dev tools). While all participants were able to complete all
tasks with hints, this obviously does not mean they could have completed
the task unassisted. Our goal was not to simply measure whether users
completed the task, but rather to gain qualitative insight into the
barriers they faced.

\hypertarget{results}{%
\subsubsection{Results}\label{results}}

\emph{Unified interaction model.} Most participants took advantage of
the unified interaction model to interleave extraction and augmentation
tasks, rather than performing all extraction up front. For example, on
task 1, most participants extracted the prerequisites by demonstration,
added one or more columns to the table to perform some string operations
on the prerequisites, and then continued on to extract more information
from the web page by demonstration. Furthermore, we hypothesize that in
a less controlled setting, users would be even more likely to interleave
extraction and augmentation, since the task may be less well defined at
the beginning.

One usability issue with the unified model was that participants
sometimes got confused about how their demonstrations would affect the
contents of the table. For example, multiple participants intended to
add a new column by demonstrating an extraction, but instead
accidentally overwrote the contents of an existing column. This poses a
design challenge because the user's demonstrations occur in the website,
so they cannot directly interact with the table while demonstrating;
this suggests that the interface needs to do a better job indicating
where the results of a demonstration will be inserted.

\emph{Extracting simple data.} On the relatively simple MIT course
catalog website, all participants were able to extract the relevant data
from the page within seconds, simply performing demonstrations with a
few clicks. This suggests that when Joker's generalization algorithm
works well, it can be an effective tool for data extraction, even for
users with limited programming experience. P1 said: \emph{``you could
hover and {[}the data{]} was already selected\ldots that was very
nice''}. P3, upon seeing the tutorial for extraction by demonstration,
said \emph{``that's like black magic.''}

\emph{Extracting complex data.} On the more complex eBay website where
demonstration alone was not sufficient, results were more varied. P1,
who had no prior web development experience, struggled to complete the
task, saying that \emph{``looking at HTML is a bit much''}; this
suggests that more work could be done to make the experience usable for
novices. However, users with more web development experience were able
to use the tool to perform complex extractions, such as directly writing
CSS selectors into the formula bar. P2 and P3 both reported that Joker's
live feedback loop was easier to use and faster than other approaches to
web extraction; P3 noted that \emph{``{[}with any other approach{]}, it
would have been slower to specify and slower to validate that I
specified it correctly.''}

It was challenging for some participants to switch between using the
browser's developer tools and the Joker interface when doing complex
extraction tasks. While we chose not to build HTML inspection into the
Joker UI because the browser already provides a very rich set of tools,
users sometimes were not able to tell how elements in the Joker table
corresponded to elements in the browser's element inspector.

\emph{Writing formulas.} In general, participants were able to learn the
formula language by using an autocomplete dropdown with inline
documentation, which we developed as part of the Joker extension. In
some cases, participants were able to immediately construct correct
formulas on the first try; in other cases it took several attempts and
some hints from the moderator to try a relevant function. While better
documentation and error messages could help improve the learnability of
the formula language, we also did not find it surprising that
participants required some time to learn a completely unfamiliar formula
language.

\hypertarget{cognitive-dimensions-analysis}{%
\subsection{Cognitive Dimensions
Analysis}\label{cognitive-dimensions-analysis}}

We analyzed Joker using the Cognitive Dimensions of Notation
\citep{blackwell2001}, a heuristic evaluation framework that has been
used to evaluate programming languages and visual programming systems
\citep{satyanarayan2014, satyanarayan2014a, ledo2018}. When contrasting
our tool with other scraping and customization tools, we find
particularly meaningful differences along several dimensions:

\emph{Progressive evaluation.} In Joker, a user can see the intermediate
results of their extraction and augmentation work at any point, and
adjust their future actions accordingly. The table user interface makes
it easy to inspect the intermediate results and notice surprises like
missing values.

In contrast, traditional extraction typically requires editing the code,
manually re-running it, and inspecting the results in an unstructured
textual format, making it harder to progressively evaluate the results.
Also, many end-user extraction tools \citep{chasins2018, lin2009}
require the user to demonstrate all the data extractions they want to
perform before showing any information about how those demonstrations
will generalize across multiple examples.\footnote{This is an instance
  where Joker's limitation of only scraping a single page at a time
  proves beneficial. All the relevant data is already available on the
  page without further network requests, making it possible to support
  progressive evaluation with low latency. Other tools that support
  scraping across multiple pages necessarily require a slower feedback
  loop.}

\emph{Premature commitment.} Many scraping tools require making a
\emph{premature commitment} to a data schema: first, the user extracts a
dataset, and then they perform augmentations using that data. Wildcard
suffered from this problem: when writing code for extraction, a user
would need to anticipate all future augmentations and extract the
necessary data.

Joker instead supports extracting data \emph{on demand}. The user can
decide on their desired augmentations and extract data as needed to
fulfill those tasks. There is never a need to eagerly guess what data
will be needed in advance.

We have also borrowed a technique from spreadsheets for avoiding
premature commitment: default naming. New data columns are automatically
assigned a single-letter name, so that the user does not need to
prematurely think of a name before extracting the data. We have not yet
implemented the capability to optionally rename demonstrated columns,
but it would be straightforward to do so, and would provide a way to
offer the benefits of names without requiring a premature commitment.

\emph{Provisionality.} Joker makes it easy to try out an extraction
action without fully committing to it. When the user hovers over any
element in a website, they see a preview of how that data would be
extracted into the table, and then they can click if they'd like to
proceed. This makes it feel very fast and lightweight to try scraping
different elements on the page.

\emph{Viscosity.} Some scraping tools have high viscosity: they make it
difficult to change a single part of an extraction specification without
modifying the global structure. For example, in Rousillon
\citep{chasins2018}, changing the desired demonstration for a single
column of a table requires re-demonstrating all of the columns. In
contrast, Joker allows a user to change the specification for a single
column of a table without modifying the others, resulting in a lower
viscosity in response to changes.

@@

Joker builds on existing work in end-user web customization, end-user
web scraping and program synthesis.

@@

Sifter \citep{huynh2006} is a tool that augments websites with advanced
sorting and filtering functionality. It attempts to automatically detect
items and fields on the website with a variety of heuristics. If these
fail, it gives the user the option of demonstrating to correct some
parts of the result. In contrast, Joker makes fewer assumptions about
the structure of websites, by giving control to the user from the
beginning of the process and displaying an editable synthesized program.
We hypothesize that focusing on a tight feedback loop rather than
automation may support a scraping process that offers more expressive
power and extends to a greater variety of websites, but further user
testing is required to validate this hypothesis. Of course, better
heuristics could benefit our model as well; the ideal system would make
good guesses while giving the user full understanding and control of the
extraction process.

@@

Mayer et al propose a user interaction model called \emph{Program
Navigation} \citep{mayer2015} which aims to give users another mechanism
beside examples for guiding the generalization process of PBE tools like
FlashExtract \citep{le2014} and FlashFill \citep{harris}. This is
important because demonstrations are an ambiguous specification for
program synthesis \citep{peleg2018}: the set of synthesized programs for
a demonstration can be very large. The Program Navigation UI displays a
natural language description of a space of possible programs, and lets
the user choose different alternatives for parts of the generated
expression. Joker shares the general idea of displaying synthesized
programs, but only presents the top-ranked program; our tool might be
improved by showing more candidate programs.

More broadly, Joker's use of PBD to generate editable code embodies Ravi
Chugh's notion of \emph{prodirect manipulation} \citep{chugh2016a},
which aims to bridge the divide between programmatic and direct
manipulation. The Sketch-N-Sketch system \citep{chugh2016} provides
prodirect manipulation by allowing users to create an SVG shape via
traditional programming and then switch to modifying its size or shape
via direct manipulation.

@@

In this paper, we presented a unified interaction model for web
customization. Our key idea is a spreadsheet formula language that
encompasses both extraction and augmentation tasks, along with a
programming-by-demonstration (PBD) interface that makes it easy for
end-users to program to create formulas. This unified interaction model
allows end-users to move seamlessly between extraction and augmentation,
resulting in a more iterative and free-form workflow for web
customization.

The main area of future work involves making the formula language more
accessible to end-users not familiar with CSS selectors. FlashProg
offers some clues through its use of natural language descriptions to
explain synthesized extraction programs. One avenue for explaining CSS
selectors could be by extracting semantic web content associated with
the elements they select, as seen in systems like Thresher
\citep{hogue2005}.

Our ultimate goal is to enable anyone that uses the web to customize
websites in the course of their daily use in an intuitive and flexible
way. This will in turn make the malleability of the web a reality for
all of its users.

\newpage

\bibliographystyle{IEEEtran}
\bibliography{references-bibtex.bib}

\end{document}

>>>>

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%%
%% IMPORTANT NOTICE:
%%
%% For the copyright see the source file.
%%
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%%
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%%
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf,10pt]{acmart}

\settopmatter{printfolios=true}

@@

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}
\pagenumbering{gobble}
%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Joker: A Unified Interaction Model For Web Customization}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.

%\author{Kapaya Katongo}
%\affiliation{%
%  \institution{MIT CSAIL}
%  \city{Cambridge, MA}
%  \country{USA}
%}
%\email{kkatongo@mit.edu}

%\author{Geoffrey Litt}
%\affiliation{%
%  \institution{MIT CSAIL}
%  \city{Cambridge, MA}
%  \country{USA}
%}
%\email{glitt@mit.edu}

%\author{Kathryn Jin}
%\affiliation{%
%  \institution{MIT CSAIL}
%  \city{Cambridge, MA}
%  \country{USA}
%}
%\email{kjin@mit.edu}

%\author{Daniel Jackson}
%\affiliation{%
% \institution{MIT CSAIL}
%  \city{Cambridge, MA}
%  \country{USA}
%}
%\email{dnj@csail.mit.edu}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
% \renewcommand{\shortauthors}{Trovato and Tobin, et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
%% \begin{abstract}
%%  
%% \end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
%% From HERE
%%\begin{CCSXML}
%%<ccs2012>
%%<concept>
%%<concept_id>10011007.10011006.10011066.10011069</concept_id>
%%<concept_desc>Software and its engineering~Integrated and visual development environments</concept_desc>
%%<concept_significance>500</concept_significance>
%%</concept>
%%</ccs2012>
%%\end{CCSXML}

%% \ccsdesc[500]{Software and its engineering~Integrated and visual development environments}
% To HERE

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
%% \keywords{end-user programming, software customization, web scraping, programming-by-example, program synthesis}

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
% \begin{teaserfigure}
%  \includegraphics[width=\textwidth]{sampleteaser}
%  \caption{Seattle Mariners at Spring Training, 2010.}
%  \Description{Enjoying the baseball game from the third-base
%  seats. Ichiro Suzuki preparing to bat.}
%  \label{fig:teaser}
%\end{teaserfigure}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

@@

Section~\ref{sec:examples} describes a concrete scenario, showing how
Joker enables a user to complete a useful customization task. In
Section~\ref{sec:implementation}, we outline the implementation of our
formula language and user interface, as well as the algorithms used by
our PBD interface. We evaluate our approach in
Section~\ref{sec:evaluation} by describing a suite of case studies in
which we used Joker to extract and augment a variety of websites in
order to characterize its capabilities and limitations. Joker relates to
existing work not only in end-user web customization, but also in
end-user web scraping and program synthesis, which we discuss in
Section~\ref{sec:related-work}. Finally, we discuss opportunities for
future work in Section~\ref{sec:conclusion}.

@@

In this section, we describe Joker's formula language in more detail.
Then, we briefly outline the \emph{wrapper induction}
\citep{kushmerick2000} algorithm that Joker's PBD interface uses to
synthesize the row element and column selectors presented in formulas.

@@

When users demonstrate a specific column value to extract, Joker must
synthesize a program that reflects the user's general intent. This is an
instance of the \emph{wrapper induction} problem of synthesizing a web
data extraction query from examples. Prior work on this topic
\citep{kushmerick2000, furche2016} prioritizes accuracy and robustness
to future changes, which makes sense for a fully automated system, but
can lead to very complex queries. In our work, we chose to prioritize
the readability of queries by less sophisticated users, so that users
can more easily author queries and repair them when they break. We
implemented a set of heuristics inspired by Vegemite \citep{lin2009} for
wrapper induction, illustrated in Figure~\ref{fig:overview}.

@@

We evaluate our interaction model and tool by describing the results of
our use of Joker to extract data and perform customizations on popular
websites. For the websites on which Joker can be used, we provide the
sequence of interactions needed to achieve the customizations; for the
websites on which Joker fails, we explain the relevant limitations.

\hypertarget{successful-applications}{%
\subsection{Successful Applications}\label{successful-applications}}

@@

\emph{Filtering titles of publications on Google Scholar.} We have also
found Joker can be useful for filtering a website's listings based on
the text content of an element in the listing. For example, we have used
Joker to filter the titles of a researcher's publications on their
Google Scholar profile which is not natively supported. First, a user
can extract the titles into a column (\texttt{A}) by demonstration.
Then, the user can write the formula \texttt{Includes(A,\ "compiler")}
that returns whether or not the title contains the keyword ``compiler.''
Finally, the user can sort by this column to get all of the publications
that fit their constraint at the top of the page. We have also used
Joker to filter other text-based directory web pages such as Google
search results and the MIT course catalog, in similar ways.

@@

\hypertarget{limitations}{%
\subsection{Limitations}\label{limitations}}

@@

@@

@@

Sifter \citep{huynh2006} is a tool that augments websites with advanced
sorting and filtering functionality. It attempts to automatically detect
items and fields on the website with a variety of heuristics. If these
fail, it gives the user the option of demonstrating to correct some
parts of the result. In contrast, Joker makes fewer assumptions about
the structure of websites, by giving control to the user from the
beginning of the process and displaying an editable synthesized program.

@@

Mayer et al propose a user interaction model called \emph{Program
Navigation} \citep{mayer2015} which aims to give users another mechanism
beside examples for guiding the generalization process of PBE tools like
FlashExtract \citep{le2014} and FlashFill \citep{harris}. This is
important because demonstrations are an ambiguous specification for
program synthesis \citep{peleg2018}: the set of synthesized programs for
a demonstration can be very large. Joker shares the general idea of
displaying synthesized programs, but only presents the top-ranked
program.

More broadly, Joker's use of PBD to generate editable code embodies Ravi
Chugh's notion of \emph{prodirect manipulation} \citep{chugh2016a},
implemented in Sketch-N-Sketch \citep{chugh2016}, which aims to bridge
the divide between programmatic and direct manipulation.

@@

In this paper, we presented a unified interaction model for web
customization. Our key idea is a spreadsheet formula language that
encompasses both extraction and augmentation tasks, along with a
programming-by-demonstration (PBD) interface that makes it easy for
end-users to program to create formulas. The main area of future work
involves making the formula language more accessible to end-users not
familiar with CSS selectors. Our ultimate goal is to enable anyone that
uses the web to customize websites in the course of their daily use in
an intuitive and flexible way.

% \printbibliography

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{references-bibtex.bib}

\end{document}
\endinput
%%
%% End of file `sample-sigconf.tex'.
